Declarative runtime reconfiguration of pulverised distributed systems \thanks{Identify applicable funding agency here. If none, delete this.}

### 2023-05-11 paper-2023-acsos-pulverization.tex
Structuring rw sec

This work provides 
 \acp{dsl}
 for specifying 
 distributed systems and
 corresponding deployment plans,
 and a framework for executing
 deployment plans and reconfigurations.
%
Therefore, this work deals 
 with multiple problems,
 investigated by multiple research threads.
%

@@

\subsection{Application description languages: component models and pulverisation}
%

\subsection{Infrastructure and deployment description languages}

\subsection{Automatic deployment and reconfiguration}
%
A comprehensive conceptual framework
 on automatic deployment of distributed systems
 is provided in a 2015 survey by Arcangeli et al. \cite{DBLP:journals/jss/ArcangeliBL15}.
%
A more recent survey by Coullon et al. focusses
 on formal techniques for verifying the correctness of reconfigurations
 in component-based distributed software systems~\cite{coullon2023swreconfig}.
%
In the \emph{osmotic computing} approach~\cite{DBLP:journals/computer/VillariFDRJR19},
 microservices (the solvent)
 can migrate across 
 the edge-cloud infrastructure (the solution),
 passing through layer boundaries (the semi-permeable membranes),
 in order to keep a balance in the desired properties (the solute).

>>>>

This work provides 
 \acp{dsl}
 for specifying 
 distributed systems and
 corresponding deployment plans,
 and a framework for executing
 deployment plans and reconfigurations.
%
Therefore, this work deals 
 with multiple problems and perspectives,
 investigated by multiple research threads.
%
In~\cite{DBLP:journals/jss/ArcangeliBL15},
the problem of (automatic) deployment of distributed software system is studied by considering
 (i) the nature of software to be deployed,
 (ii) the nature of the deployment domain (i.e. the available infrastructure),
 (iii) how the deployment is designed,
 and 
 (iv) how the deployment is performed.
%
Accordingly, 
 we cover related works about
 languages for 
 specifying applications (\Cref{sec:rw:whatsw}),
 languages for specifying infrastructures and deployments (\Cref{sec:rw:depdesc}),
 and
 techniques for automatic deployment and reconfiguration (\Cref{sec:rw:autodep}).

\subsection{Application description languages: component models and pulverisation}
\label{sec:rw:whatsw}
%
A comprehensive survey on component-based software engineering is provided in~\cite{vale2016component-based-se}.

@@

\subsection{Infrastructure and deployment description languages}
\label{sec:rw:depdesc}

\subsection{Automatic deployment and reconfiguration}
\label{sec:rw:autodep}
%
A comprehensive conceptual framework
 on automatic deployment of distributed systems
 is provided in a 2015 survey by Arcangeli et al. \cite{DBLP:journals/jss/ArcangeliBL15}.
%
A more recent survey by Coullon et al. focusses
 on formal techniques for verifying the correctness of reconfigurations
 in component-based distributed software systems~\cite{coullon2023swreconfig}.
%
In the \emph{osmotic computing} approach~\cite{DBLP:journals/computer/VillariFDRJR19},
 microservices (the solvent)
 can migrate across 
 the edge-cloud infrastructure (the solution),
 passing through layer boundaries (the semi-permeable membranes),
 in order to keep a balance in the desired properties (the solute).
